Towards Pandemic-Scale Ancestral Recombination Graphs of SARS-CoV-2

### 2023-05-19 paper.tex
Reasonable version of the intro

It is important to note that the exact endpoints of intervals can be
somewhat arbitrary, since they are defined by exact comparisons
of a recombinant's parents. The presence of problematic sites that are enriched
for errors will therefore tend to artificially truncate breakpoint intervals
at these sites.
It is therefore helpful to compare the number of interecting intervals
with the number of mutations per site in Figure~\ref{fig:breakpoint-distribution}.
For example, position 28,271 (located in the ORF8-N intergenic
region) has the largest number of mutations and corresponds to the
left endpoint of 9 intervals and the right of 57.
The 7,572 mutations  (including 5,782 insertions and 1,605 deletions)
at this site are a likely indicator that this
homopolymeric region is prone to sequencing errors
and should be included in the list of ``problematic sites'' that
are excluded from analysis (Section~\ref{sec:data_preprocessing}).
% There can be good biological reasons for this too though
However, hypermutable sites such as 27,972 \citep{Jungreis2021-dh}
have the same effect of truncating intervals. At this site we have
770 mutations (including 425 C$>$T, 314 T$>$C) with potential signals
of polymorphism maintained by selection [FIXME!!], and 58 intervals
with endpoints within one base of this site.

>>>>

It is important to note that the exact endpoints of intervals can be
somewhat arbitrary, since they are defined by exact comparisons
of a recombinant's parents. The presence of problematic sites that are enriched
for errors will therefore tend to artificially truncate breakpoint intervals
at these sites.
It is therefore helpful to compare the number of interecting intervals
with the number of mutations per site in Figure~\ref{fig:breakpoint-distribution}.
For example, position 28,271 (located in the ORF8-N intergenic
region) has the largest number of mutatations and corresponds to the
left endpoint of 9 intervals and the right of 57.
The 7,572 mutations  (including 5,782 insertions and 1,605 deletions)
at this site are a likely indicator that this
homopolymeric region is prone to sequencing errors
and should be included in the list of ``problematic sites'' that
are excluded from analysis (Section~\ref{sec:data_preprocessing}).
% There can be good biological reasons for this too though
However, hypermutable sites such as 27,972 \citep{Jungreis2021-dh}
have the same effect of truncating intervals. At this site we have
770 mutations (including 425 C$>$T, 314 T$>$C) with potential signals
of polymorphism maintained by selection [FIXME!!], and 58 intervals
with endpoints within one base of this site.
